NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-11 ms_nihao_budget.tex
fix some details

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from central galaxy
where the stars are rare, for a given halo the four phases add up to
unity.  All simulations share a common attribute.  The cold gas (T$<
10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K
$<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
in the whole corona region.  For higher mass galaxies, warm-hot gas
dominates the corona  which signals higher efficiency  of feedback.
Even beyond the virial radius, the cool and warm-hot gas has similar
features as the gas within virial radius which reveals the gas
surrounding galaxies within large distance is the major reservoir of
baryons.

@@

Fig.~\ref{fig:rps} shows the mass ratio profiles of total baryons  for
each simulation. Here the y-axis is the ratio between the baryonic to
dark matter mass, $M_{\rm b}(<R) / M_{\rm dm}(<R)$, enclosed
within a sphere of radius, $R$, normalized by the cosmic
baryon-to-dark matter ratio, $\Omega_{\rm b}/\Omega_{\rm dm}$.

>>>>

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from central galaxy
where the stars are rare, for a given halo the four phases add up to
unity, {\bf each line is colour coded to the virial mass}.  
All simulations share a common attribute.  The cold gas (T$<
10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K
$<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$)
in the whole corona region.  For higher mass galaxies, warm-hot gas
dominates the corona  which signals {\bf stronger virial shock} and
higher efficiency  of feedback.
Even beyond the virial radius, the cool and warm-hot gas has similar
features as the gas within virial radius which reveals the gas
surrounding galaxies within large distance is the major reservoir of
baryons.

@@

Fig.~\ref{fig:rps} shows the {\bf cumulative fraction} of total baryons  for
each simulation. Here the y-axis is the ratio between the baryonic to
dark matter mass, $M_{\rm b}(<R) / M_{\rm dm}(<R)$, enclosed
within a sphere of radius, $R$, normalized by the cosmic
baryon-to-dark matter ratio, $\Omega_{\rm b}/\Omega_{\rm dm}$.
